### 2025-09-25 paper/sec/evaluation.tex
small tweak

\emph{The results show that the system is robust when provided with sufficient guidance but degrades when underspecified.} With the target-value sharing, 
the InterpretationAgent produced correct Fluid expressions in 74.9\%  (S.D. 3.0\%) of cases,
but performance dropped to 57.1\% when the target was withheld. This highlights the system's reliance on explicit cues when resolving ambiguous fragments.

>>>>

The results show that \emph{the system is robust when provided with sufficient guidance but degrades when underspecified.} With the target-value sharing, 
the InterpretationAgent produced correct Fluid expressions in 74.9\%  (S.D. 3.0\%) of cases,
but performance dropped to 57.1\% when the target was withheld. This highlights the system's reliance on explicit cues when resolving ambiguous fragments.
